\chapter{Background}
\label{ch:background}

To ensure a uniform understanding of the methods and technologies used, important definitions of terms are given in this chapter.
Furthermore, various contents are presented, which underlie our approach and are important for its understanding.
Since our approach deals exclusively with \acp{KG}, a more precise definition of the term is first given in \Autoref{sec:knowledge_graphs}.
Another important part is the \acp{KGE}, which map the information in the form of entities and relations of the KG in a low-dimensional vector space.
Therefore, different embedding models and their differences are presented in \Autoref{sec:knowledge_graph_embeddings}.
All of them have different training objectives which can mathematically represented by different loss-function which have to be optimized during the training time.
Their definition is given in \Autoref{sec:training_objective_types}.
Besides Negative Sampling, there are other methods for training \ac{KGE} models.
For their differentiation, these are first introduced in \Autoref{sec:training_techniques} and in the course of this, an exact definition of Negative Sampling is given. 
Subsequently, different Negative Sampling methods from the literature and their categories described in \Autoref{sec:negativesamplingmethods}  and in particular one approach is presented in more detail (\Autoref{sec:kbgan}, which provides the basis for our later approach.
In \Autoref{sec:evaluating_knowledge_graph_embeddings}, different methods are presented how to measure the accuracy of the learned embeddings.
Finally, Uncertainty Sampling and its different approaches and measurements are presented in the end of this chapter (\Autoref{sec:uncertaintysampling}).


\input{content/chapters/02_background/sections/01_knowledge_graphs}

\input{content/chapters/02_background/sections/02_knowledge_graph_embeddings}

\input{content/chapters/02_background/sections/03_training_objective_types}

\input{content/chapters/02_background/sections/04_training_techniques}

\input{content/chapters/02_background/sections/05_negative_sampling_methods}

\input{content/chapters/02_background/sections/06_kbgan}

\input{content/chapters/02_background/sections/07_evaluating_knowledge_graph_embeddings}

\input{content/chapters/02_background/sections/08_uncertainty_sampling}













