\chapter{Background}
\label{ch:background}

\section{Problem Analysis} \label{sec:problemanalysis}
% general introduction
Since \acp{KG} contain large amount of information, they provide many application possibilities.
However, to achieve good results for these applications we need to learn good embeddings which represent as much information as possible in a graph representation of a low-dimensional vector space.
Most of graph representation learning methods can be unified within a \ac{SampledNCE} framework comprising an encoder that generates node embeddings by learning to distinguish pairs of a positive and a negative triple \cite{MCNS}.
Therefore, we need negative triples for embedding learning which are not available in most \acp{KG} 

For this reason, we are left with two options to collect them \cite{safavi2021negater}: 
On one hand they can be obtained by human annotation which is very cost-prohibitive at scale, but leads to very informative and useful examples. 
On the other, they can be generated ad-hoc, which in turn does not represent a great effort, but also leads to uninformative and useless negative examples.
For this reason, we need to find a way between these two extreme approaches.

% Static Distribution-Based Sampling
\textit{Static Distribution-Based Sampling} (\autoref{sec:negativesamplingmethods}) approaches are commonly used because of their simplicity and efficiency, but ignore the dynamics in the Negative Sampling distribution which lead to the vanishing gradient problem \cite{qianunderstanding}.
This problem occurs when the gradient will be vanishingly small and accordingly, small gradients prevent changing the weight value.
This can impede the training process or, in the worst case, completely stop the model from further training.
While negative triples, such as those generated by randomly replacing a head or tail entity, are very likely to be negative examples, they are generally uninformative and useless.
For example, by replacing the tail entity in given positive triple (Paderborn, locatedIn, Germany) by randomly selected entity 'Apple' leads to the new negative triplet (Paderborn, locatedIn, Apple).
Even though it is a true negative triple, it is uninformative and useless for embedding learning.
The problem with 'too easy' negative triples is less severe to models using log-softmax loss function, because they usually sample a high amount of negatives for one positive triple \cite{cai2017kbgan}.
However, the performance of marginal loss functions can be seriously damaged by the low quality of uniformly sampled negatives since negative-to-positive ratio is always 1:1 \cite{cai2017kbgan}.

% Custom Cluster-Based Sampling
To get more efficiency in the training process and to search for suitable entities in a more targeted way is aimed with  \textit{Custom Cluster-Based Sampling} methods (\autoref{sec:negativesamplingmethods}).
By selecting negative samples only from a handful of candidates and not from the entire entity set, a better correlation between the positive and corresponding negative triple is expected.
This negative triple should be closer to the original positive triple and thus provide more valuable information for the \ac{KGE} model.
For example, Domain Sampling \cite{domainSampling} is to sample from the same domain.
For example, if it is recognized that 'Germany' is a country and that 'France' is a nearby country, the much more valuable negative triple (Paderborn, locatedIn, France) could be sampled from the  positive triple (Paderborn, locatedIn, Germany).
However, as \acp{KG} grow rapidly and are updated frequently, continuous renewing custom clusters is essential and difficult \cite{qianunderstanding}.

With these approaches of Negative Sampling from a fixed distribution two more different problems arise:
Since they ignore changes in the distribution of negative triples, they suffer from the vanishing gradient and biased estimation problem \cite{zhang2021efficient}.
The scoring functions tend to give observed (positive) triplets large values and most of the non-observed (probably negative) triplets will have smaller values during the training.
Therefore, if negative triplets are uniformly sampled, it is very likely to pick up one with zero gradients.
This leads to the following main challenges for Negative Sampling \cite{zhang2021efficient}: 
(i) The negative triple's dynamic distribution has to be captured and 
(ii) triples have to be effectively sampled from this distribution.

% Dynamic Distribution-Based sampling
To capture the dynamic distribution of the negative triples, the
group of \textit{Dynamic Distribution-Based Sampling} (\autoref{sec:negativesamplingmethods}) was developed.
The two approaches \ac{KBGAN} \cite{cai2017kbgan} and \ac{IGAN} \cite{IGAN} are considered as pioneering works of these Sampling methods and attempt to address the challenge of capturing the negative distribution by a \ac{GAN} \cite{zhang2021efficient}.
\acp{GAN} were originally proposed for generating examples in a continuous space such as images and adapted for the generation of hard negative examples \cite{zhang2021efficient}.
Using an adversarial training process like in \ac{KBGAN} described in \autoref{sec:kbgan}, the distribution of negative triples is thus determined.
However, this is not an efficient training process and it is not effectively sampled from this distribution.
Additionally, it increases the number of training parameters because of the generator and the model suffers from instability and degeneracy.
This results from the fact, that the \textsc{REINFORCE} gradient has high variance for training the generator and only a few negative triples lead to large gradient \cite{zhang2021efficient}.
Consequently, the \ac{GAN}-based models have to put a lot of effort to model the negative triple distribution which leads to instable performances.
Since the generator and discriminator in Negative Sampling only draw information from the two underlying embedding models, pre-training is necessary, which is a time-consuming endeavor.
However, even if only a few triple pairs (negative + positive triple) are useful for learning embedding, they are not maintained to be able to learn from them at a later time.
Moreover, no other information of the graph is included except the softmax-probability outputs of the generator and the \ac{KGE} model of the discriminator.
Randomly selecting one of the negative triples does not ensure that a useful one is selected.
For embedding, the distinction between negative and positive triples from areas of a \ac{KG} about which no or incomplete information are available could be particularly important.

In summary, there are already several approaches for Negative Sampling, but they still have problems to capture the dynamic distribution of the negative triples or effectively sample them \cite{zhang2021efficient}.
Therefore, we present a new Negative Sampling technique which aims to \textbf{improve the efficiency of Sampling by selecting more informative and useful negative examples for the embedding model by uncertainty}.

